Proposal: Loose Grammar Inference for Lossy Compression

### 2012-10-18 proposal.tex
added compilatio script
Reflow

\begin{abstract}
Test (\cite{sequitur})
\end{abstract}

@@

There has also been very interesting work analyzing how grammar based algorithms compare with
the theoretical best lossless grammar for a string, in the line of \cite{approximate}. However,
these analytic bounds for lossless grammars are outside the scope of our proposed research.

@@

>>>>

@@

There has also been very interesting work analyzing how grammar based
algorithms compare with the theoretical best lossless grammar for a string, in
the line of \cite{approximation}. However, these analytic bounds for lossless
grammars are outside the scope of our proposed research.

@@

There are two important metrics in evaluating our
